### 2024-10-22 manuscript.tex
Various improvements

@@

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
%\setmainfont{Crimson Text}
%\setmainfont{CrimsonText}[
%	Path=./fonts/,
%	Extension=.ttf,
%	UprightFont=*-Regular,
%	BoldFont=*-Bold,
%	ItalicFont=*-Italic,
%	BoldItalicFont=*-BoldItalic
%]
%\setmonofont[Scale=0.8]{Space Mono}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
%\renewcommand{\bibsection}{\section*{Publications}}
\parskip=6pt
\parindent=0pt

@@

TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
Energy System (CERES) instruments on board of the Terra and Aqua satellites
\citep{wielicki1996,loeb2018}. In our analysis we use the adjusted all sky SW
and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
clouds 1 degree daily edition 4A product
(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
\citep{doelling2013,doelling2016}.

Radiation calculations presented in the results (Section \ref{sec:results})
were done in such a way that they always represent averages of daily means.
This is done in order to be consistent with the CERES SYN1deg data, which are
available as daily means. Therefore, every instantaneous profile in the
simulated lidar data is assigned a daily mean radiation value corresponding to
the day (in the Coordinated Universal Time; UTC). In turn, the average
radiation during the entire voyage or station observation period is calculated
as the average of the profile values. In the observed lidar data, the daily
mean radiation value is taken from the spatially and temporally co-located
CERES SYN1deg data of the day (in UTC). The voyage or station average is
calculated in the same way.

@@

Precipitation can cause strong enough lidar backscattering to be recognised as
a cloud by the threshold-based cloud detection method used in the ALCF. This is
undesirable if equivalent precipitation backscatter is not included in the
simulated lidar profiles. It was not possible to include precipitation
simulation in the ALCF due to the absence of required fields in the ICON model
output and the reanalysis data (the liquid and ice precipitation mass mixing
ratios), and because the required radiation calculations for precipitation are
currently not implemented in the ALCF. In order to achieve a fair comparison of
observations with models, one should exclude observed and simulated lidar
profiles with precipitation either manually or using an automated method. It is
relatively difficult to distinguish precipitation backscatter from cloud
backscatter in lidar observations, especially when only one wavelength channel
and no polarised channel are available. In models, the same can be accomplished
relatively easily by excluding profiles exceeding a certain amount of surface
precipitation flux. In the observations, using precipitation flux measurements
from rain gauges can be very unreliable on ships due to ship movement and
turbulence caused by nearby ship structures. Our analysis of rain gauge data
from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge
time series and human-performed synoptic observations, as well as large
inconsistencies in the rain gauge time series. Human-performed observations of
precipitation presence or absence are expected to be reliable, but only cover a
limited set of time instants. Therefore, it was desirable to implement a method
of detecting precipitation from observed backscatter profiles alone.

@@

Here, we briefly describe the results of the cyclonic activity and stability
distribution, which is relavant for the subsequent analaysis, because these
conditions are used for subsetting our dataset. Fig.
\ref{fig:cyclone-stability}a shows a geographical distribution of the fraction
of cyclonic days as determined by the cyclone tracking algorithm applied on the
ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
expected, the strongest cyclonic activity is in the high-latitude SO zone, and
it is relatively zonally symmetric at all latitudes.  While both reanalysis and
the model agree relatively well, differences in the strength of the local
extremes of occurrence are notable, especially over the Amundsen Sea, which is
more cyclonic in the reanalysis, and around Cape Adere, which is more cyclonic
in ICON. There differences might, however, stem from the relatively short time
periods of comparison (4 year) and the fact that the model is free running.

Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the
relatively stable and unstable conditions as determined by the LTS (Section
\ref{sec:cyclone-stability}).  The relatively unstable conditions are prevalent
in the mid SO (50--65°S), which might be explained by the relatively cold
near-surface air overlying relatively warm sea surface. The relatively stable
conditions are prevalent elsewhere over the SO. The distribution is also less
zonally symmetric than the cyclonic activity.  In the high-latitude SO, the
presence of sea ice might have substantial stabilising effect
\citep{knight2024}. The ERA5 renalysis is also substantially more stable than
ICON across the whole region.

@@

We used the ALCF to derive cloud occurrence by height and the total cloud
fraction from observations, ICON, and the two reanalyses, ERA5 and MERRA-2
(Fig.  \ref{fig:cloud-occurrence-panel}). We aggregated the data sources
(voyages, campaigns and stations) by calculating the averages and percentiles
of all individual profiles (Fig.  \ref{fig:cloud-occurrence}). The analysis
shows that the total cloud fraction (determined as the fraction of profiles
with clouds at any height in the lidar cloud mask) is underestimated in ICON
and reanalyses by about 10\% and 20\%, respectively. In particular, ICON
overestimates cloud occurrence below 1 km and underestimates it above, MERRA-2
underestimates cloud occurrence at all heights, especially near the surface,
and ERA5 simulates cloud occurrence relatively well above 1 km, but strongly
underestimates it near the surface.  We note that fog or near-surface clouds
are strongly lacking in the reanalyses.  As shown in Fig.
\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
the data sources and longitudes. The ICON results are overall better matching
the observations than the reanalyses.

In the general case (Fig. \ref{fig:cloud-occurrence}a), the observations show
cloud occurrence peaking at the surface, whereas models show a higher peak (at
about 500 m). The models underestimate the total cloud fraction by 10--20\% and
show a strong drop in cloud occurrence near the surface, but this is not
supported by the observations. ICON and ERA5 overestimate cloud occurrence at
the peak (between 0--1 km). Above 1 km, ICON and MERRA-2 understimate cloud
occurrence, but ERA5 is very accurate. The too high peak in models is partly
supported by the LCL distribution, which peaks higher in the models than in the
observations (at the surface), although this is not very pronounced.

@@

In all situations, even when the models overestimate cloud occurrence at some
altitudes, they always substantially underestimate the total cloud fraction.
ICON can be generally characterised as substantially overestimating cloud
occurrence below 1 km and underestimating above, underestimating the total
cloud fraction, and showing greatest biases in the relatively unstable and
non-cyclonic condititions. It also shows a peak of cloud occurrence at higher
altitude than obs (500 m vs. near the surface), and correspondingly, its LCL
tends to be also higher. MERRA-2 can be generally characterised as
underestimating cloud occurrence at nearly all altitudes as well as the total
cloud fraction, but mostly above and below 500 m (the peak at 500 m is
well-represented). It struggles the most in the low-latitude SO zone and in the
relatively unstable situations. ERA5 can be generally characterised as
representing cloud occurrence correctly above about 1--1.5 km, overestimating
below, but underestimating near-surface cloud occurrence (0--500 m). The total
cloud fraction is strongly understimated in all situations. It has a tendency
towards understimation in the low-latitude SO zone and the relatively unstable
situations, conversely, overestimating in the high-latitude SO zone and the
relatively stable conditions.

@@

\subsection{Cloud cover}

@@

In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
as in the previous section. Observations show the greatest representation of
high cloud cover (5--8 oktas), peaking at 7 oktas. This is not represented by
ICON or the reanalyses.  While ICON is the closest, it tends to be 1 okta
clearer the observations, peaking at 6 oktas, and highly understimating days
with 8 oktas.  Overall, the reanalyses show results similar to each other,
underestimating cloud cover by about 2 oktas, and strongly understimating days
with 7 and 8 oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud
cover and thus is more consistent with observations.

When analysed by subsets, the cyclonic subset shows the highest cloud cover,
with 8 oktas occurring on one half of such days (Fig. \ref{fig:cloud-cover}d).
This is not represented by ICON or the reanalyses at all. Interestingly, clear
sky days (0 oktas) also have a local maximum peaking at about 15\% in this
subset.  When we contrast the low- and high-latitude zones, we see that the
high-latitude zone tends to have greater cloud cover, peaking at 8 oktas (Fig.
\ref{fig:cloud-cover}c). The high-latitude zone also has almost no clear sky or
small cloud cover cases (0--4 oktas). ICON and the reanalyses represent at
least this characteristic of the distribution well for 0--3 oktas, but
otherwise show bises similar to the general case. One of the greatest biases is
present in ERA5 in the relatively unstable subset, in which ERA5 peaks at 3
oktas, whereas the observations peak at 7 oktas and show negligible cloud cover
below 5 oktas.

@@

We analysed about 2300 radiosonde profiles south of 40°S from the 24 RV
\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
temporally colocated profiles were taken from ICON and the reanalyses. Because
the time period of the ICON model output was different from the observations,
model time was chosen to be the same as the radiosonde launch time relative to
the start of the year. The profiles were partitioned into the same subsets as
the lidar observations: all, 40--55°S, 55+°S, cyclonic, non-cyclonic, stable,
and unstable. The groups 40--55°S and 55+°S, cyclonic and non-cyclonic, and
stable and unstable were mutually exclusive in pairs. Apart from relative
humidity, we focus on comparing virtual potential temperature ($\theta_v$) due
to its role in low-level tropospheric stability, being one of the primary
factors affecting shallow convection and the associated low-level cloud
formation and dissipation. The observed and model profiles of virtual potential
temperature are shown in Fig. \ref{fig:potential-temperature}.

@@

We acknowledge the RV \emph{Polarstern} datasets provided by the Alfred Wegener
Institute and Pangaea, the AA15-16 dataset provided by the Australian Antarctic
Division (AAD) and University of Canterbury (UC), RV \emph{Tangaroa} datasets
provided by the National Institute of Water and Atmospheric Research and UC,
the NBP1704 dataset provided by the National Science Foundation, Cooperative
Institute for Research in Environmental Sciences, University of Colorado and
UC, the HMNZSW16 dataset provided by the Royal New Zealand Navy and UC, the
MARCUS dataset provided by the Atmospheric Radiation Measurement (ARM) and AAD,
and the MICRE dataset provided by ARM, the Australian Bureau of Meteorology,
and AAD. We thank the scientific staff, the crew, and everyone involved in
collecting data on the voyages and stations, especially Kelly Schick, Peter
Guest, John J.  Cassano, Simon Parsons, Graeme Plank, Sally Garrett, Jamie
Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.  Alexander and Alex
Schuddeboom. We acknowledge the ICON model output provided by the nextGEMS
project and the DKRZ, reanalysis dataset ERA5 provided by the Copernicus
Climate Change Service and MERRA-2 provided by the Global Modeling and
Assimilation Office. We acknowledge supercomputing resources provided by the
DKRZ.  We dedicate this study to the memory of Mike J. Harvey, who very
substantially contributed to obtaining the atmospheric observations on the RV
\emph{Tangaroa} voyages used in this study.

>>>>

% Related publications:
%

@@

\documentclass[12pt,a4paper]{article}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=2cm]{geometry}
\usepackage[citecolor=black]{hyperref}
\usepackage[authoryear,round]{natbib}
\usepackage{doi}
\usepackage{titlesec}
\usepackage{caption}
\DeclareCaptionLabelSeparator{pipe}{ | }
\captionsetup{labelfont={bf,sf},labelsep=pipe}
\usepackage{graphicx}
\usepackage{lineno}
\linenumbers
\setsansfont{Source Sans Pro}
\setmainfont{EB Garamond}
\setmonofont[Scale=0.8]{SpaceMono}[
	Path=./fonts/,
	Extension=.ttf,
	UprightFont=*-Regular,
	BoldFont=*-Bold,
	ItalicFont=*-Italic,
	BoldItalicFont=*-BoldItalic
]
\hypersetup{
	colorlinks=true,
	urlcolor=blue,
	pdftitle={Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses},
	pdfauthor={Peter Kuma, Frida A.-M. Bender, …}
}
\bibliographystyle{abbrvnat}
\titleformat*{\section}{\large\bfseries\sffamily}
\titleformat*{\subsection}{\normalsize\bfseries\sffamily}
\titlespacing*{\section}{0pt}{14pt}{6pt}
\titlespacing*{\subsection}{0pt}{13pt}{4pt}
\parskip=6pt
\parindent=0pt

@@

TOA radiation quantities are taken from the Clouds and the Earth’s Radiant
Energy System (CERES) instruments on board of the Terra and Aqua satellites
\citep{wielicki1996,loeb2018}. In our analysis we used the adjusted all sky SW
and LW upwelling fluxes at TOA from the synoptic TOA and surface fluxes and
clouds 1 degree daily edition 4A product
(CER\_SYN1deg-Day\_Terra-Aqua-MODIS\_Edition4A)
\citep{doelling2013,doelling2016}.

Radiation calculations presented in the results (Section \ref{sec:results})
were done in such a way that they always represent averages of daily means.
This was done in order to be consistent with the CERES SYN1deg data, which are
available as daily means. Therefore, every instantaneous profile in the
simulated lidar data was assigned a daily mean radiation value corresponding to
the day (in the Coordinated Universal Time; UTC). In turn, the average
radiation during the entire voyage or station observation period were
calculated as the average of the profile values. In the observed lidar data,
the daily mean radiation value was taken from the spatially and temporally
co-located CERES SYN1deg data of the day (in UTC). The voyage or station
average was calculated in the same way.

@@

Precipitation can cause strong enough lidar backscattering to be recognised as
clouds by the threshold-based cloud detection method used in the ALCF. This is
undesirable if equivalent precipitation backscatter is not included in the
simulated lidar profiles. It was not possible to include precipitation
simulation in the ALCF due to the absence of required fields in the ICON model
output and the reanalysis data (the liquid and ice precipitation mass mixing
ratios), and because the required radiation calculations for precipitation are
currently not implemented in the ALCF. In order to achieve a fair comparison of
observations with models, one should exclude observed and simulated lidar
profiles with precipitation either manually or using an automated method. It is
relatively difficult to distinguish precipitation backscatter from cloud
backscatter in lidar observations, especially when only one wavelength channel
and no polarised channel are available. In models, the same can be accomplished
relatively easily by excluding profiles exceeding a certain amount of surface
precipitation flux. In the observations, using precipitation flux measurements
from rain gauges can be very unreliable on ships due to ship movement and
turbulence caused by nearby ship structures. Our analysis of rain gauge data
from the RV \emph{Tangaroa} showed large discrepancies between the rain gauge
time series and human-performed synoptic observations, as well as large
inconsistencies in the rain gauge time series. Human-performed observations of
precipitation presence or absence are expected to be reliable, but only cover a
limited set of time instants. Therefore, it was desirable to implement a method
of detecting precipitation from observed backscatter profiles alone.

@@

Here, we briefly describe the results of the cyclonic activity and stability
distribution, which is relavant for the subsequent analaysis, because these
conditions are used for subsetting our dataset. Fig.
\ref{fig:cyclone-stability}a shows a geographical distribution of the fraction
of cyclonic days as determined by the cyclone tracking algorithm applied on the
ERA5 reanalysis and ICON data (Section \ref{sec:cyclone-stability}). As
expected, the strongest cyclonic activity is in the high-latitude SO zone, and
it is relatively zonally symmetric at all latitudes.  While both reanalysis and
the model agree relatively well, differences in the strength of the local
extremes of occurrence are notable, especially over the Amundsen Sea, which is
more cyclonic in the reanalysis, and around Cape Adere, which is more cyclonic
in ICON. These differences might, however, stem from the relatively short time
periods of comparison (4 year) and the fact that the model is free-running.

Fig. \ref{fig:cyclone-stability}b shows a geographical distribution of the
relatively stable and unstable conditions as determined by the LTS (Section
\ref{sec:cyclone-stability}).  The relatively unstable conditions are prevalent
in the middle SO (50--65°S), which might be explained by the relatively cold
near-surface air overlying relatively warm sea surface. The relatively stable
conditions are prevalent elsewhere over the SO. The distribution is also less
zonally symmetric than the cyclonic activity.  In the high-latitude SO, the
presence of sea ice might have substantial stabilising effect
\citep{knight2024}. The ERA5 renalysis is also substantially more stable than
ICON across the whole region.

@@

We used the ALCF to derive cloud occurrence by height and the total cloud
fraction from observations, ICON, ERA5 and MERRA-2 (Fig.
\ref{fig:cloud-occurrence-panel}). In addition, we aggregated the data sources
(voyages and stations) by calculating the averages and percentiles of all
individual profiles, presented in Fig. \ref{fig:cloud-occurrence}. The analysis
shows that the total cloud fraction (determined as the fraction of profiles
with clouds at any height in the lidar cloud mask) is underestimated in ICON
and the reanalyses by about 10\% and 20\%, respectively. When analysed by
height, ICON overestimates cloud occurrence below 1 km and underestimates it
above, MERRA-2 underestimates cloud occurrence at all heights, especially near
the surface, and ERA5 simulates cloud occurrence relatively well above 1 km,
but strongly underestimates it near the surface.  We note that fog or
near-surface clouds are strongly lacking in the reanalyses (fog and clouds are
both included in the cloud occurrence).  As shown in Fig.
\ref{fig:cloud-occurrence-panel}, the biases are relatively consistent across
the data sources and longitudes. We conclude that the ICON results are overall
better matching the observations than the reanalyses in this metric.

In the general case (Fig. \ref{fig:cloud-occurrence}a), the observations show
cloud occurrence peaking at the surface, whereas models show a higher peak (at
about 500 m). The models underestimate the total cloud fraction by 10--20\% and
show a strong drop in cloud occurrence near the surface, but this is not
supported by the observations. ICON and ERA5 overestimate cloud occurrence at
the peak (between 0--1 km). Above 1 km, ICON and MERRA-2 understimate cloud
occurrence, but ERA5 is very accurate. The too high peak in models is partly
supported by the lifting condensation level (LCL) distribution, which peaks
higher in the models than in the observations (at the surface), although this
is not very pronounced.

@@

In all situations, even when the models overestimate cloud occurrence at some
altitudes, they always substantially underestimate the total cloud fraction.
ICON can be generally characterised as substantially overestimating cloud
occurrence below 1 km and underestimating above, underestimating the total
cloud fraction, and showing greatest biases in the relatively unstable and
non-cyclonic condititions. It also shows a peak of cloud occurrence at higher
altitude than observations (500 m vs. near the surface), and correspondingly,
its LCL tends to be also higher. MERRA-2 can be generally characterised as
underestimating cloud occurrence at nearly all altitudes as well as the total
cloud fraction, but mostly above and below 500 m (the peak at 500 m is
well-represented). It struggles the most in the low-latitude SO zone and in the
relatively unstable situations. ERA5 can be generally characterised as
representing cloud occurrence correctly above about 1--1.5 km, overestimating
below, but underestimating near-surface cloud occurrence (0--500 m). The total
cloud fraction is strongly understimated in all situations. It has a tendency
towards understimation in the low-latitude SO zone and the relatively unstable
situations, conversely, overestimating in the high-latitude SO zone and the
relatively stable conditions.

@@

\subsection{Cloud cover}
\label{sec:cloud-cover}

@@

In Fig.  \ref{fig:cloud-cover} we show the results for the same subsets of data
as in the previous section. Observations have the greatest representation of
high cloud cover (5--8 oktas), peaking at 7 oktas. This is not represented by
ICON or the reanalyses.  While ICON is the closest, it tends to be 1 okta
clearer the observations, peaking at 6 oktas, and highly understimating days
with 8 oktas.  Overall, the reanalyses show results similar to each other,
underestimating cloud cover by about 2 oktas, and strongly understimating days
with 7 and 8 oktas. Of the two reanalyses, MERRA-2 shows slightly higher cloud
cover and thus is more consistent with observations.

When analysed by subsets, observations in the cyclonic subset show the highest
cloud cover, with 8 oktas occurring on one half of such days (Fig.
\ref{fig:cloud-cover}d).  This is not represented by ICON or the reanalyses at
all. Interestingly, clear sky days (0 oktas) also have a local maximum peaking
at about 15\% in this subset.  When we contrast the low- and high-latitude
zones, we see that the high-latitude zone tends to have greater cloud cover,
peaking at 8 oktas (Fig.  \ref{fig:cloud-cover}c). The high-latitude zone also
has almost no clear sky or small cloud cover cases (0--4 oktas). ICON and the
reanalyses represent at least this characteristic of the distribution well for
0--3 oktas, but otherwise show bises similar to the general case. One of the
greatest biases is present in ERA5 in the relatively unstable subset, in which
ERA5 peaks at 3 oktas, whereas the observations peak at 7 oktas and show
negligible cloud cover below 5 oktas.

@@

We analysed about 2300 radiosonde profiles south of 40°S from the 24 RV
\emph{Polarstern} voyages, MARCUS, NBP1704, TAN1702, and TAN1802. Spatially and
temporally colocated profiles were taken from ICON and the reanalyses. Because
the time period of the ICON model output was different from the observations,
model time was chosen to be the same as the radiosonde launch time relative to
the start of the year. The profiles were partitioned into the same subsets as
above (Sections \ref{sec:cloud-occurrence} and \ref{sec:cloud-cover}).  Apart
from relative humidity, we focus on comparing virtual potential temperature
($\theta_v$) due to its role in low-level tropospheric stability, being one of
the primary factors affecting shallow convection and the associated low-level
cloud formation and dissipation. The observed and model profiles of virtual
potential temperature are shown in Fig. \ref{fig:potential-temperature}.

@@

PK and FB received funding from the European Union’s Horizon 2020 research and
innovation programme under a grant agreement no. 101003470 and supercomputing
resources were provided by the DKRZ (project 1125 ICON-development) and the
National Academic Infrastructure for Supercomputing in Sweden (allocation
2023/22-202).  We acknowledge the RV \emph{Polarstern} datasets provided by the
Alfred Wegener Institute and Pangaea, the AA15-16 dataset provided by the
Australian Antarctic Division (AAD) and University of Canterbury (UC), RV
\emph{Tangaroa} datasets provided by the National Institute of Water and
Atmospheric Research and UC, the NBP1704 dataset provided by the National
Science Foundation, Cooperative Institute for Research in Environmental
Sciences, University of Colorado and UC, the HMNZSW16 dataset provided by the
Royal New Zealand Navy and UC, the MARCUS dataset provided by the Atmospheric
Radiation Measurement (ARM) and AAD, and the MICRE dataset provided by ARM, the
Australian Bureau of Meteorology, and AAD. We thank the scientific staff, the
crew, and everyone involved in collecting data on the voyages and stations,
especially Kelly Schick, Peter Guest, John J.  Cassano, Simon Parsons, Graeme
Plank, Sally Garrett, Jamie Halla, Sean Hartery, Mike J.  Harvey (†), Simon P.
Alexander and Alex Schuddeboom. We acknowledge the ICON model output provided
by the nextGEMS project and the DKRZ, reanalysis dataset ERA5 provided by the
Copernicus Climate Change Service and MERRA-2 provided by the Global Modeling
and Assimilation Office.  Last but not least, we acknowledge the use of open
source software Python, Cython \citep{behnel2011}, TensorFlow
\citep{abadi2016}, Devuan GNU+Linux, parallel \citep{tange2011}, NumPy
\citep{harris2020}, SciPy \citep{virtanen2020}, Matplotlib \citep{hunter2007},
cartopy \citep{cartopy}, pyproj, Inkscape, Bash, GNU Fortran, HDF
\citep{folk1999}, and NetCDF \citep{rew1990}.  We dedicate this study to the
memory of Mike J.  Harvey, who very substantially contributed to obtaining the
atmospheric observations on the RV \emph{Tangaroa} voyages used in this study.
